Codes for exploratory analysis

### 2025-03-21 code/eda-code/eda.qmd
changed to numeric

```{r}
# Define dataset
df <- data_2010

>>>>

```{r}
# Define dataset

df <- data_2010

df$Current_health_expenditure_per_capita_current_US <- as.numeric(df$Current_health_expenditure_per_capita_current_US)
df$GDP_growth_annual_ <- as.numeric(df$GDP_growth_annual_)
df$Income_share_held_by_lowest_20 <- as.numeric(df$Income_share_held_by_lowest_20)
df$Control_of_Corruption_Estimate <- as.numeric(df$Control_of_Corruption_Estimate)
df$Life_expectancy_at_birth_total_years <- as.numeric(df$Life_expectancy_at_birth_total_years)
df$Literacy_rate_adult_total__of_people_ages_15_and_above <- as.numeric(df$Literacy_rate_adult_total__of_people_ages_15_and_above)
df$Trade__of_GDP <- as.numeric(df$Trade__of_GDP)
df$Foreign_direct_investment_net_inflows_BoP_current_US <- as.numeric(df$Foreign_direct_investment_net_inflows_BoP_current_US)
df$Age_dependency_ratio__of_workingage_population <- as.numeric(df$Age_dependency_ratio__of_workingage_population)
